Building Markov State Models for Periodically Driven Non-Equilibrium Systems

### 2015-02-10 writedown/period.noneq.msm/coverletter/letter-jctc.tex
backup

In this paper, we demonstrate how to build the Markov state model
(MSM) for the non-equilibrium systems under a periodic external
driving.  The MSM reproduces the essential long timescale
conformational dynamics of the original system, and at the same time
it does not require the ergodicity of each single molecular
trajectory.  Therefore, it does not only describes, but also provides
more insightful understanding of the non-equilibrium system than the
standard analyses of the molecular trajectories.  Our methods are
tested and validated by an example non-equilibrium system: The alanine
dipeptide under periodic electric field.

@@

As experts who can judge the validity of the work we suggest the
following names:
\begin{itemize}\itemsep -1pt
\item Vijay Pande, Stanford University, pande@stanford.edu
\item John Chodera, Memorial Sloan Kettering Cancer Center, choderaj@mskcc.org
\item Giovanni Ciccotti,  University of Rome La Sapienza, Giovanni.Ciccotti@roma1.infn.it
\end{itemize}

>>>>

In this paper, we demonstrate how to build the Markov state model
(MSM) for the non-equilibrium systems under a periodic external
driving.  The MSM reproduces the long-timescale
conformational dynamics of the non-equilibrium system, and at the same time
it does not require the ergodicity of each single molecular
trajectory.  Therefore, it does not only describes, but also provides
more insightful understanding of the non-equilibrium system than the
standard analyses of the molecular trajectories.  Our methods are
tested and validated by an example non-equilibrium system: The alanine
dipeptide under periodic electric field.

@@

As experts who can judge the validity of the work we suggest the
following names:
\begin{itemize}\itemsep -1pt
\item Vijay Pande, Stanford University
  % , pande@stanford.edu
\item John Chodera, Memorial Sloan Kettering Cancer Center
  % , choderaj@mskcc.org
\item Giovanni Ciccotti,  University of Rome La Sapienza
  % , Giovanni.Ciccotti@roma1.infn.it
\end{itemize}
